Modelling BCG vaccination in the UK

### 2019-12-02 rmds/index.Rmd
add install of tinytex

---
author: 'Samuel Abbott'
date: 'August 2019'
division: 'Bristol Medical School\: Population Health Sciences'
advisor: 'Ellen Brooks Pollock'
altadvisor: 'Hannah Christensen'
department: 'Faculty of Health Sciences'
title: 'Modelling BCG vaccination in the UK'
subtitle: 'What is the impact of changing policy?'
wordcount: "55,287"
knit: "bookdown::render_book"
site: "bookdown::bookdown_site"
always_allow_html: yes
output: 
  ##Thesis can only be fully built for pdf using the makefile
  #thesisdown::thesis_pdf: default
  thesisdown::thesis_gitbook: default
  #thesisdown::thesis_word: default
  #thesisdown::thesis_epub: default
bibliography: ["bib/thesis.bib"]
#Download your specific bibliography database file and refer to it in the line above.
link-citations: yes
colorlinks: yes
csl: ["csl/bmj.csl"]
#Download your specific csl file and refer to it in the line above.
lot: true
lof: true
space_between_paragraphs: true
#Delete the # at the beginning of the previous line if you'd like
#to have a blank new line between each paragraph
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}

>>>>

---
abstract: |
  `r if(knitr:::is_latex_output()) paste(readLines("00-abstract.Rmd"), collapse = ' ')`
acknowledgements: |
  `r if(knitr:::is_latex_output()) paste(readLines("00-acknowledgements.Rmd"), collapse = ' ')`
declaration: |
  `r if(knitr:::is_latex_output()) paste(readLines("00-declaration.Rmd"), collapse = ' ')`
contribution: |
  `r if(knitr:::is_latex_output()) paste(readLines("00-contribution.Rmd"), collapse = ' ')`
acronyms: |
  `r if(knitr:::is_latex_output()) paste(readLines("00-acronyms.Rmd"), collapse = ' ')`
author: 'Samuel Abbott'
date: 'August 2019'
division: 'Bristol Medical School\: Population Health Sciences'
advisor: 'Ellen Brooks Pollock'
altadvisor: 'Hannah Christensen'
department: 'Faculty of Health Sciences'
title: 'Modelling BCG vaccination in the UK'
subtitle: 'What is the impact of changing policy?'
wordcount: "55,287"
knit: "bookdown::render_book"
site: "bookdown::bookdown_site"
always_allow_html: yes
output: 
  ##Thesis can only be fully built for pdf using the makefile
  #thesisdown::thesis_pdf: default
  thesisdown::thesis_gitbook: default
  #thesisdown::thesis_word: default
  #thesisdown::thesis_epub: default
bibliography: ["bib/thesis.bib"]
#Download your specific bibliography database file and refer to it in the line above.
link-citations: yes
colorlinks: yes
csl: ["csl/bmj.csl"]
#Download your specific csl file and refer to it in the line above.
lot: true
lof: true
space_between_paragraphs: true
#Delete the # at the beginning of the previous line if you'd like
#to have a blank new line between each paragraph
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
